### 2012-06-13 inst/examples/Reed.Rmd
hmm, plotting constant escapement

``` {r  profit}
profit <- profit_harvest(price=1, c0 = 0.1) 
````

@@

``` {r }
qplot(x_grid, opt$D[,1], xlab="stock size", ylab="harvest")
````

@@

``` {r  parallel}
require(snowfall) 
sfInit(parallel=TRUE, cpu=4)
sethi_SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
sethi_opt <- find_dp_optim(sethi_SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

We can take a look at the stochastically estimated policy function,

``` {r }
qplot(x_grid, sethi_opt$D[,1], xlab="stock size", ylab="harvest")
````

>>>>

``` {r  profit}
profit <- profit_harvest(price=1, c0 = 0.0001) 
````

@@

``` {r }
qplot(x_grid, x_grid[opt$D[,1]], xlab="stock size", ylab="harvest")
````

Note that this corresponds to constant optimal escapement, 
``` {r }
qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
````

@@

``` {r  parallel, eval=FALSE}
require(snowfall) 
sfInit(parallel=TRUE, cpu=4)
sethi_SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
sethi_opt <- find_dp_optim(sethi_SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
qplot(x_grid, sethi_opt$D[,1], xlab="stock size", ylab="harvest")
````
